|

### 2022-12-20 paper_comparison/paper_comparison/paper_comparison.Rmd
add mosaic plot

(top: curves)
(middle: dots)
(bottom: vertical lines/grid lines)

@@

tick mark on x. dashed line too strong. use solid line (grey) in light color.

@@

>>>>

@@

@@

```{r}
library(ggmosaic)
vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(type = ifelse(type == "polynomial", "non-linearity", type)) %>%
  left_join(vi_survey %>% 
           count(unique_lineup_id) %>%
           rename(num_subject = n)) %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  mutate(conv_reject = ifelse(conventional_p_value < 0.05, "Reject", "Not reject"),
         reject = ifelse(p_value < 0.05, "Reject", "Not reject")) %>%
  ggplot() +
  ggmosaic::geom_mosaic(aes(x = ggmosaic::product(conv_reject, reject), fill = conv_reject)) +
  xlab("Visual tests") +
  ylab("Conventional tests") +
  labs(fill = "Conventional tests")
```
